%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom output flags
\usepackage{etoolbox}
\newtoggle{projects}
\toggletrue{projects}
\newtoggle{oldjobs}
\togglefalse{oldjobs}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Joel Gallant} \\ \vspace{1pt}
    \small 306-450-8803 $|$ \href{mailto:x@x.com}{\underline{joelmgallant@gmail.com}} $|$
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/joelmgallant}} $|$
    \href{https://github.com/...}{\underline{github.com/joelmgallant}}
\end{center}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart


    \resumeSubheading
      {VP, Development}{May 2020 -- Present}
      {Swarmio Media}{Halifax, NS}
      \resumeItemListStart
        \resumeItem{Lead platform technical design and delivery strategy across multiple applications.}
        \resumeItem{Represent technical stakeholders in high-level business priority and planning sessions.}
        \resumeItem{Implement continuous integration and deployment on cloud-agnostic Kubernetes clusters.}
        \resumeItem{Maintain organization-wide roadmap for software offerings.}
        \resumeItem{Create and evolve development and business processes for high efficiency and value delivery.}
        \resumeItem{Direct teams across technology stacks and business units to achieve product and organization goals.}
      \resumeItemListEnd

      \resumeSubheading
      {Software Development Manager}{September 2018 -- May 2020}
      {Swarmio Media}{Halifax, NS}
      \resumeItemListStart

        \resumeItem{Building and leading a team to deliver innovative end-to-end platform solutions for the global Esports industry.}
        \resumeItem{Implementing agile development processes and tools throughout the organization and product line.}
        \resumeItem{Evolving legacy platform components to meet emerging business and technical demands.}
        \resumeItem{Lead design and transition to heterogenous microservice-based platform architecture and declarative delivery pipelines.}

      \resumeItemListEnd


      \resumeSubheading
      {Technical Director}{March 2012 -- September 2018}
      {Telos Entertainment}{Charlottetown, PE}
      \resumeItemListStart
        \resumeItem{Technical design \& execution of video games and services for a wide variety of platforms and clients.}
        \resumeItem{Research and development of prototype software and third-party software integration.}
        \resumeItem{Distributed systems deployment \& administration, network configuration \& monitoring.}
        \resumeItem{Project planning \& reporting, client requirements gathering \& negotiation.}
        \resumeItem{Team management, hiring and organizational structures.}

      \resumeItemListEnd

    \resumeSubheading
      {Game Developer}{March 2009 -- March 2012}
      {Telos Entertainment}{Charlottetown, PE}
      \resumeItemListStart
        \resumeItem{Technical design \& development of internal and contract game titles.}
        \resumeItem{Unity/C\#: Desktop/Mobile/Web/SDK}
        \resumeItem{Objective-C/Java: Native extensions}
        \resumeItem{AS3/Javascript: Web/Mobile}
        \resumeItem{Java/Ruby/NodeJS: Backend Services}
      \resumeItemListEnd

% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Game Developer}{March 2009 -- March 2012}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
%-------------------------------------------

      \iftoggle{oldjobs}{

        \resumeSubheading
          {Software Developer}{April 2008 -- December 2008}
          {Timeless Technologies}{Charlottetown, PE}
          \resumeItemListStart
            \resumeItem{Created and maintained web-based systems and product sites for external clients.}
          \resumeItemListEnd

        \resumeSubheading
          {Programmer / Analyst}{January 2007 -- August 2007}
          {Public Services and Procurement Canada}{Gatineau, Quebec}
          \resumeItemListStart
            \resumeItem{Created and maintained prototype database-driven web systems for internal department use.}
            \resumeItem{Maintaining and updating existing applications.}
            \resumeItem{Configuring and deploying application servers.}
            \resumeItem{Interface design and implementation for prototype sites.}
          \resumeItemListEnd



        \resumeSubheading
          {Software Engineering Intern }{May 2006 -- September 2006}
          {Kodak Technical Services, Inc}{Summerside, PE}
          \resumeItemListStart
            \resumeItem{Software testing and defect resolution.}
            \resumeItem{Design \& development of in-house software tools.}
            \resumeItem{Hardware \& software setup and technical support.}
          \resumeItemListEnd
      }

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {University of Prince Edward Island}{Charlottetown, PE}
    {Bachelor of Science in Computer Science, Co-operative Education Program}{2005--2010}
    \resumeSubheading
      {Bluefield High}{PE}
      {High School Diploma, graduated with honors}{2001--2004}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\iftoggle{projects}{
  \section{Projects}
      \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
            \resumeItemListStart
              \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
              \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
              \resumeItem{Visualized GitHub data to show collaboration}
              \resumeItem{Used Celery and Redis for asynchronous tasks}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
            \resumeItemListStart
              \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
              \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
              \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
              \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
            \resumeItemListEnd
      \resumeSubHeadingListEnd

}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, Java, Scala, Python, SQL / NoSQL, TypeScript/JavaScript, HTML/CSS } \\
     \textbf{Frameworks}{: Play, Spring Boot, React, Node.js } \\
     \textbf{Developer Tools}{: Git, Visual Studio (+Code), IntelliJ IDEA, Xcode, Emacs, (neo)vim } \\
     \textbf{Deployment Tools}{: Docker, Kubernetes, ArgoCD, GitLab } \\
     \textbf{Media}{: Adobe Creative Suite, Davinci Resolve, Blender}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
